Brownian Dynein Model

### 2015-08-21 latex/derivation.tex
Add labels to derivation.tex system equations.
Add half-made changes to derivation.tex to correctly compute angular velocity matrix terms.

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} - L_{t}\cos(\Theta_{mr}) \\
  X_{br} &= X_{mr} - L_{s}\cos(\Theta_{br})
\end{align}

\begin{align}
  Y_{bl} &= 0 \\
  Y_{ml} &= Y_{bl}+L_{s}\sin(\Theta_{bl}) \\
  Y_{t}  &= Y_{ml}+L_{t}\sin(\Theta_{ml}) \\
  Y_{mr} &= Y_{t} +L_{t}\sin(\Theta_{mr}-\pi) = Y_{t} + \mn L_{t}\sin(\Theta_{mr}) \\
  Y_{br} &= Y_{mr}+L_{s}\sin(\Theta_{br}-\pi) = Y_{mr}+ \mn L_{s}\sin(\Theta_{br})
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                          
  \dot{Y}_{bl} &= 0 \\                                                        
  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bl} &= 0 \\                                                               
  \dot{Y}_{ml} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
\end{align}

@@

\section{System after Addition}
By adding equations from our system together we can isolate the $\lambda$ values. \\

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) =
\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) =
\dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) =
\dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+ \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{equation}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) = 
\dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\end{equation}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) =
\dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
+ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) =
\dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) =
\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
- R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{equation}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) = \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\end{equation}%Fix'd

\section{Solution for $\dot{\Theta}_{br}$}
The following sections come up with solutions for $\dot{\Theta}_{br}$, $\dot{\Theta}_{mr}$, $\dot{\Theta}_{ml}$ and $\dot{\Theta}_{bl}$ using the equations we found in the previous section. \\

\begin{multline}
\Big (\dot{X}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big) \frac{1}{(X_{br} - X_{mr})} = \mn\frac{1}{\gamma}\lambda_{rs}
= \Big (\dot{Y}_{mr} - L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big) \frac{1}{(Y_{br} - Y_{mr})}
\end{multline}

\begin{multline}
\Big (L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
= \Big (\mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr}) + \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr})
\end{multline}

\begin{multline}
\Big (L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(Y_{br} - Y_{mr}) + \Big (L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} \Big)(X_{br} - X_{mr})
= \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
\end{multline}

\begin{multline}
\dot{\Theta}_{br} \Bigg(\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr}) \Bigg )
= \Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(Y_{br} - Y_{mr})
\end{multline}

\begin{equation}
\dot{\Theta}_{br} = \frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(X_{br} - X_{mr}) - \Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} 
- R_{xbr} \Big)(Y_{br} - Y_{mr})}{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)(Y_{br} - Y_{mr}) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)(X_{br} - X_{mr})}
\end{equation}

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)\frac{(Y_{br} - Y_{mr})}{(X_{br} - X_{mr})} + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)\frac{(X_{br} - X_{mr})}{(Y_{br} - Y_{mr})}}
\end{equation}

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big)\frac{L_{s}\sin(\Theta_{br}-\pi)}{L_{s}\cos(\Theta_{br}-\pi)} + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)\frac{L_{s}\cos(\Theta_{br}-\pi)}{L_{s}\sin(\Theta_{br}-\pi)}}
\end{equation}

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)}
{\Big (\frac{{L_{s}}^2\sin^2(\Theta_{br}-\pi)}{L_{s}\cos(\Theta_{br}-\pi)}\Big) + \Big (L_{s}\cos(\Theta_{br}-\pi) \Big)}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)}
{\Big (L_{s}\sin(\Theta_{br}-\pi) \Big) + \Big (\frac{{L_{s}}^2\cos^2(\Theta_{br}-\pi)}{L_{s}\sin(\Theta_{br}-\pi)} \Big) }
\end{equation}

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{s}\cos(\Theta_{br}-\pi))}
{\Big( {L_{s}}^2\sin^2(\Theta_{br}-\pi)\Big) + \Big ({L_{s}}^2\cos^2(\Theta_{br}-\pi) \Big)}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{br}-\pi))}
{\Big ({L_{s}}^2\sin^2(\Theta_{br}-\pi) \Big) + \Big( {L_{s}}^2\cos^2(\Theta_{br}-\pi) \Big) }
\end{equation}

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{s}\cos(\Theta_{br}-\pi))}
{{L_{s}}^2}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{br}-\pi))}
{{L_{s}}^2}
\end{equation}
\\
Now expand the cartesian velocity definition: \\

\begin{multline}
\dot{\Theta}_{br} =
\frac{1}{L_{s}}\Big(\mn L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi) \\
+ \frac{1}{L_{s}}\Big(L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
\end{multline}

\section{Solution for $\dot{\Theta}_{mr}$}

>>>>

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{t}\cos(\Theta_{mr}-\pi) = X_{t} - L_{t}\cos(\Theta_{mr}) \\
  X_{br} &= X_{mr}+L_{s}\cos(\Theta_{br}-\pi) = X_{mr} - L_{s}\cos(\Theta_{br})
\end{align}

\begin{align}
  Y_{bl} &= 0 \\
  Y_{ml} &= Y_{bl}+L_{s}\sin(\Theta_{bl}) \\
  Y_{t}  &= Y_{ml}+L_{t}\sin(\Theta_{ml}) \\
  Y_{mr} &= Y_{t} +L_{t}\sin(\Theta_{mr}-\pi) = Y_{t} - L_{t}\sin(\Theta_{mr}) \\
  Y_{br} &= Y_{mr}+L_{s}\sin(\Theta_{br}-\pi) = Y_{mr} - L_{s}\sin(\Theta_{br})
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \dot{X}_{bl} - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \dot{X}_{ml} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                          
  \dot{Y}_{bl} &= 0 \\                                                        
  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bl} &= 0 \\                                                               
  \dot{Y}_{ml} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
\end{align}

@@

\section{System after Addition}
By adding equations from our system together we can isolate the $\lambda$ values. This system has been verified via CAS.\\

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) =
\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Ax}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) =
\dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Bx}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) =
\dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+ \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Cx}
\end{equation}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) = 
\dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Dx}
\end{equation}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) =
\dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
+ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Ay}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) =
\dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:By}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) =
\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
- R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Cy}
\end{equation}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) = \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Dy}
\end{equation}%Fix'd

\section{Creating Angular Velocity Matrix}

Our goal is to take the above system of equations and put it in this form:

where $X_1$, $X_2$, $X_3$ and $X_4$ contain only force terms and no unknown $\lambda$s. We accomplish this by taking the above system of equations, equating terms with equal lambda terms to eliminate lambdas, and rearranging.

\subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
Here we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} = X_1$

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls} =
\Big(\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)\frac{1}{(X_{ml} - X_{bl})}
\end{multline}

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{ls} =
\Big( \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr}
+ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)\frac{1}{(Y_{ml} - Y_{bl})}
\end{multline}

\begin{multline}
\Big(\dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} - R_{xbr} - \frac{1}{\gamma}F_{xbr}\Big)(Y_{ml} - Y_{bl}) = \\
\Big( \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} \\
+ \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} - R_{ybr} - \frac{1}{\gamma}F_{ybr}\Big)(X_{ml} - X_{bl})
\end{multline}

\begin{multline}
\Big(\dot{X}_{bl} + \dot{X}_{ml} + \dot{X}_{t } + \dot{X}_{mr} 
- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} \\
- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bl})) = \\
\Big(\dot{Y}_{bl} + \dot{Y}_{ml} + \dot{Y}_{t } + \dot{Y}_{mr}
+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} \\
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
\end{multline}

\begin{multline}
\Big(
- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl}
- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml}
- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr}\\
- L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } -\frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr}
- R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)(L_s\sin(\Theta_{bl})) = \\
\Big(
+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl}
+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml}
+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr}\\
+ L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr}
- R_{yml} - R_{yt} - R_{ymr} - R_{ybr}\Big)(L_s\cos(\Theta_{bl}))
\end{multline}
